\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/introduction.tex

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of USB, named \tool.  \tool
extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional HIDs like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass many countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of USB attacks based on our approach to verify its effectiveness,
including scripting, remote control, and privacy extraction.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the USB devices they
plugged in for security purposes.  After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated UI rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}

>>>>

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of USB, named \tool.  \tool
extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
capable to transfer video stream data, \tool could obtain the information of
victim's graphical interface during attacks.  Combining it with the emulation
of traditional HIDs like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass many countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of USB attacks based on our approach to verify its effectiveness,
including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the USB devices they
plugged in for security purposes.  
10 volunteers are involved in the user study.
At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated UI rendering, to separate the user interface
into sensitive and insensitive layers.  Only content on the insensitive layer
will be passed to the insecure driver and thus rendered on the external
display, which protects content on the sensitive layer.
%\shuqing{Case study, evaluation, notable results.}
